---
title: "Understanding Data Analytics II"
subtitle: "plan, apply and scale"
author: "Matthias Bannert"
date: "October 2017"
output: ioslides_presentation
widescreen: true
smaller: true
---


# Statistics and Visualization


## Basic descriptive statistics

- mean
- median
- distributions of variables
- quantiles
- standard deviation, variance

=> help to get an idea about a dataset, 
describe distribution of variables


## Basic Hypothesis Testing: t.test

1. Is mpg significantly different in 4 or 6 cylinder cars?
2. Is displacement significantly different in automatic and manual transmission cars?

=> But what if there's more than two groups? 

## Time Series Analysis: Seasonal Adjustment

- Trend component
- Seasonal component
- noise
- State of the art: X13-Arima-SEATS (US Census Bureau)


## An Introduction to Linear Regression: univariate case

```{r}
fit1 <- lm(mpg ~ wt, data = mtcars)
summary(fit1)
```

## An Introduction to Linear Regression: multivariate case

```{r}
fit2 <- lm(mpg ~ ., data = mtcars)
summary(fit2)
```

## Another Example: Car Valuation

- Insurance
- Used car market


## Trends in Data Science

- custom models can be understood by large platforms, e.g. [AzureML](https://studio.azureml.net/)
- crowd intelligence, e.g. [Kaggle competition](http://www.kaggle.com)









